Response to the defense feedback

### 2021-06-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

\begin{figure}[ht]
\centering
\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */
    shift++;
    if (BN_is_odd(X)) {
        if (!BN_uadd(X, X, n))
            goto err;
    }
    ...
    if (!BN_rshift1(X, X))  // It causes the leak severe!
        goto err;
    ...
}
\end{lstlisting}
    \caption{Previously unknown sensitive secret-dependent branch leaks from function 
             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
             function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
             shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
    \label{chapter3:fig:unknown_leakage}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{lstlisting}[xleftmargin=.1\textwidth,xrightmargin=.01\textwidth]
while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */
    shift++;
    if (BN_is_odd(X)) {
        if (!BN_uadd(X, X, n))
            goto err;
    }
    ...
    if (!BN_rshift1(X, X))  // It causes the leak severe!
        goto err;
    ...
}
\end{lstlisting}
    \caption{Previously unknown sensitive secret-dependent branch leaks from function 
             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
             function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
             shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
    \label{chapter3:fig:unknown_leakage}
\end{figure}
